%---------------------------------------------------------
% Resume in LaTeX (sb2nov template) — Jiale Lin
% Dynamically generated for Nemetschek - Network Security Engineer
% Generated on 2025-09-22 17:46:16
%---------------------------------------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\setlength{\parindent}{0pt}

% Section formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

% List formatting
\newcommand{\resumeItem}[2]{\item\small{\textbf{#1}{: }#2}}
\newcommand{\resumeSubheading}[4]{%
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small #3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-4pt}
}
\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-2pt}}
\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*, itemsep=1pt, topsep=2pt]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*, itemsep=1pt, topsep=1pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-4pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Jiale Lin} & \href{mailto:jeremykalilin@gmail.com}{jeremykalilin@gmail.com}\\
  \href{https://ljluestc.github.io}{ljluestc.github.io} & +1-510-417-5834 \\
  \href{https://linkedin.com/in/jiale-lin}{linkedin.com/in/jiale-lin} & U.S. Citizen \\
\end{tabular*}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Colorado Boulder}{}
      {Master of Science in Computer Science}{May 2025}
    \resumeSubheading
      {University of Arizona}{}
      {Bachelor in Mathematics (CS Emphasis)}{May 2019}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Aviatrix}{Santa Clara, CA}
      {Senior Software Engineer (2024–Present) | Senior MTS (2023–2024) | MTS (2022–2023)}{May 2022 -- Present}
      \resumeItemListStart
        \resumeItem{}
          {	extbf{	extbf{	extbf{	extbf{	extbf{	extbf{	extbf{	extbf{Security}}}}}}}} \& Networking: Built secure multi-cloud automation with TLS and Zero-Trust; implemented eBPF/iptables validation for firewall upgrades and DDoS mitigation; hardened supply chain with SBOM and policy gates.}
        \resumeItem{}
          {Infrastructure \& 	extbf{DevOps} Automation: Automated infrastructure with 	extbf{Terraform}; operated 	extbf{	extbf{Kubernetes}} across 	extbf{	extbf{	extbf{AWS}}}, 	extbf{	extbf{	extbf{Azure}}}, and 	extbf{	extbf{GCP}}; built 	extbf{CI/CD} with 	extbf{GitHub Actions}, 	extbf{Jenkins}, ArgoCD, and GitOps, reducing deployment time by 30%.}
        \resumeItem{}
          {	extbf{observability}: Enhanced 	extbf{	extbf{monitoring}} with 	extbf{Prometheus}, 	extbf{Grafana}, and 	extbf{DataDog}; added 	extbf{CI/CD} health signals and SLOs; reduced MTTR by 15%.}
        \resumeItem{}
          {Software Development: Developed REST/gRPC services using 	extbf{Go}, 	extbf{	extbf{	extbf{Python}}}, Bash, Kafka; optimized service boundaries, caching, and concurrency for scalability and reliability.}
      \resumeItemListEnd

    \resumeSubheading
      {Google Fiber (via Adecco)}{Mountain View, CA}
      {Test Engineer}{Jun 2019 -- Jun 2021}
      \resumeItemListStart
        \resumeItem{}
          {Infrastructure \& 	extbf{	extbf{monitoring}}: Streamlined deployments with 	extbf{	extbf{Docker}} and 	extbf{	extbf{Kubernetes}}; implemented 	extbf{Prometheus}/	extbf{Grafana} for real-time 	extbf{	extbf{monitoring}}.}
        \resumeItem{}
          {Network 	extbf{	extbf{testing}}: Performed CPE 	extbf{	extbf{testing}} with Ixia Veriwave, improving network throughput by 20%.}
        \resumeItem{}
          {Test Automation: Developed a Page Object Model framework with Selenium/WebDriver (	extbf{	extbf{	extbf{Java}}}) for Angular apps, reducing test failures by 25%.}
        \resumeItem{}
          {Automation: Automated tasks using Google Apps Script, 	extbf{	extbf{	extbf{Python}}}, and Bash, saving 15 hrs/week.}
      \resumeItemListEnd

    \resumeSubheading
      {Veeva Systems}{Pleasanton, CA}
      {Software Development Engineer in Test}{Aug 2021 -- May 2022}
      \resumeItemListStart
        \resumeItem{}
          {UI Test Automation: Automated web UI with Selenium and native iOS/Android with Appium; integrated suites into 	extbf{CI/CD} with dashboards and flaky-test quarantine.}
        \resumeItem{}
          {Process Optimization: Streamlined QA by refactoring suites and optimizing test cases, improving defect detection and reducing regression escapes.}
        \resumeItem{}
          {BDD Framework Development: Implemented a cross-platform BDD framework using Kotlin, Cucumber, and Gradle; integrated with 	extbf{Jenkins} CI to automate execution and expand coverage.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{AI-Powered Network Traffic Classifier \textnormal{(C++, Python, TF/ONNX, eBPF, gRPC, K8s)}}
      {Realtime packet/flow features via eBPF; ONNX model served over async gRPC on Kubernetes with rollout guards (shadow A/B, drift detection, canary). Qt6/Electron dashboard with rate/latency charts; CI for model eval (AUC/PR), onnxruntime CPU/GPU.}
    \resumeSubItem{Graph-based Social Recommender \textnormal{(Python, Node2Vec, FAISS, MF, Airflow)}}
      {Graph ETL → Node2Vec embeddings + matrix factorization; FAISS ANN for sub-ms top-k retrieval; offline metrics (AUC, NDCG) and online CTR lift (double-digit). Deployed as FastAPI service with Redis cache; Airflow DAGs for retraining/backfills.}
    \resumeSubItem{Algorithm Visualization Tool \textnormal{(JavaFX, k-NN, Telemetry)}}
      {Interactive 2D collision/physics visualizer with toggleable k-NN 'ML mode' vs. analytic solver; perf counters, frame timing, exportable traces — live demo.}
    \resumeSubItem{Multi-Protocol Router Sim \textnormal{(C++, FRR, BGP/OSPF/ISIS, Netem, CMake)}}
      {FRR control-plane integration; token-bucket/WFQ shaping; tc/netem impairments; gtest coverage and pcap diffing; CLI \& YAML scenarios for regression suites.}
  \resumeSubHeadingListEnd

\end{document}